Photographic Text-to-Image Synthesis \\ with a Hierarchically-nested Adversarial Network

### 2017-11-14 cvpr2018.tex
st

\textbf{Visual-semantic similarity~}
\textcolor{red}{Since the aforementioned evaluation methods can not measure alignment between the generated images and the text description, we introduce a new qualitative measurement, namely visual-semantic similarity (VS similarity) inspired by \cite{vsemb}.} Denote $\bm{v}$ as the feature vector extract by a pre-trained CNN model $f_{cnn}$ (Inception-v2 \cite{inception} pre-trained on Imagenet), and $\bm{t}$ denote the text embedding. 
We define a scoring function $s(\bm{x}, \bm{y})=\frac{\bm{x}\cdot \bm{y}}{||\bm{x}||\cdot ||\bm{y}||}$. 
We learn two mapping functions $f_v$ and $f_t$, which map both image and sentence embeddings into one semantic space $\mathbb{R}^{512}$, by minimizing the following bi-directional ranking loss:
\begin{equation}
\begin{split}
\mathcal{L}_{vs} &= \sum_{ \bm{v} }\sum_{ \bm{t^-} }~\max( 0, \delta- s(f_v(\bm{v}), f_t( \bm{t^-} ))) \\
&+ \sum_{ \bm{t} }\sum_{ \bm{v-} }~\max( 0,  \delta- s(f_t(\bm{t}), f_v( \bm{v^-} )))
\end{split}
\end{equation}
where $\delta$ is the margin, which is set as 0.2, every $(\bm{v}, \bm{t})$ is a ground truth image text pair, $\bm{t^-}$ denotes a mismatching text description for the image corresponding to $\bm{v}$, and vice-versa for $\bm{v^-}$. In the testing stage, given an text embedding $\bm{t}$, and the generated images $o$, the corresponding vs-similarity will be calculated as $s(f_{cnn}(o), \bm{t})$. Higher score indicates semantic consistency.

@@

\begin{table}[t] % retrieval
	\small
	\begin{minipage}[b]{0.5\linewidth}
		\begin{tabularx}{1\textwidth}{c@{\hskip1pt}|c@{\hskip1pt}|c@{\hskip1pt}}
			\specialrule{1.5pt}{0pt}{0pt}  
			Metric 			&   Inception 	 & VS   	\\  \hline
			wo/local        &   $3.12{\pm}.018$      &   $.263{\pm}.13$           \\  \hline
			w/local         &   $3.45{\pm}.07$ 	 &   $.296{\pm}.13$		    \\ \hline
		\end{tabularx}
		\vspace{-0.8cm}
	\end{minipage} %\hfill
	\begin{minipage}[b]{0.49\linewidth}
		\begin{tabularx}{.98\textwidth}{ccc|c}
			\specialrule{1.5pt}{0pt}{0pt}  
			\multicolumn{3}{c|}{Components}	&  \multirow{2}{*}{\thead{Inception \\ score}}	\\ \cline{1-3}
			64	& 128	& 256 			& 		\\ \hline
			&  		&	\checkmark	&	${3.52{\pm}.04}$	\\ 
			&  	\checkmark	&	\checkmark	&	${3.99{\pm}.04}$	\\
			\checkmark	&  			&	\checkmark	&  ${4.14{\pm}.03}$		\\
			\checkmark	&  \checkmark		&	\checkmark	&	${4.15{\pm}.05}$ \\ \hline

>>>>

\textbf{Visual-semantic similarity~}
\textcolor{red}{Since the aforementioned evaluation methods can not measure the alignment between generated images and corresponding  text descriptions, we introduce a new quantitative measurement, namely visual-semantic similarity (VS similarity) inspired by \cite{vsemb}.} Denote $\bm{v}$ as the feature vector extracted by a pre-trained CNN model $f_{cnn}$ (Inception-v2 \cite{inception} pre-trained on Imagenet), and $\bm{t}$ denote the text embedding. 
We define a scoring function $s(\bm{x}, \bm{y})=\frac{\bm{x}\cdot \bm{y}}{||\bm{x}||\cdot ||\bm{y}||}$. 
We learn two mapping functions $f_v$ and $f_t$, which map both image features and sentence embeddings into one semantic space $\mathbb{R}^{512}$, by minimizing the following bi-directional ranking loss:
\begin{equation}
\vspace{-0.2cm}
\begin{split}
\mathcal{L}_{vs} &= \sum_{ \bm{v} }\sum_{ \bm{t^-} }~\max( 0, \delta- s(f_v(\bm{v}), f_t( \bm{t^-} ))) \\
&+ \sum_{ \bm{t} }\sum_{ \bm{v-} }~\max( 0,  \delta- s(f_t(\bm{t}), f_v( \bm{v^-} )))
\end{split}
\vspace{-0.2cm}
\end{equation}

where $\delta$ is the margin, which is set as 0.2, every $(\bm{v}, \bm{t})$ is a ground truth image text pair, $\bm{t^-}$ denotes a mismatching text description for the image corresponding to $\bm{v}$, and vice-versa for $\bm{v^-}$. In the testing stage, given an text embedding $\bm{t}$, and the generated images $o$, the corresponding vs-similarity will be calculated as $s(f_{cnn}(o), \bm{t})$. Higher score indicates semantic consistency.

@@

\begin{table}[t] % retrieval
	\small
	\begin{minipage}[b]{0.5\linewidth}
		\begin{tabularx}{1\textwidth}{c@{\hskip1pt}|c@{\hskip1pt}|c@{\hskip1pt}}
			\specialrule{1.5pt}{0pt}{0pt}  
			Metric 			&   Inception 	 & VS   	\\  \hline
			wo/local        &   $3.12{\pm}.02$      &   $.263{\pm}.13$           \\  \hline
			w/local         &   $3.45{\pm}.07$ 	 &   $.296{\pm}.13$		    \\ \hline
		\end{tabularx}
		\vspace{-0.8cm}
	\end{minipage} %\hfill
	\begin{minipage}[b]{0.49\linewidth}
		\begin{tabularx}{.98\textwidth}{ccc|c}
			\specialrule{1.5pt}{0pt}{0pt}  
			\multicolumn{3}{c|}{Components}	&  \multirow{2}{*}{\thead{Inception \\ score}}	\\ \cline{1-3}
			64	& 128	& 256 			& 		\\ \hline
			&  		&	\checkmark	&	${3.52{\pm}.04}$	\\ 
			&  	\checkmark	&	\checkmark	&	${3.99{\pm}.04}$	\\
			\checkmark	&  			&	\checkmark	&  ${4.14{\pm}.03}$		\\
			\checkmark	&  \checkmark		&	\checkmark	&	${4.15{\pm}.05}$ \\ \hline
